Data preprocessing: raw data to processed data

### 2023-03-14 manuscript/manuscript.Rmd
initial draft of the manuscript with the results

```{r setup, include = FALSE, warning=FALSE, message=FALSE}
library("papaja")
library(tidyverse)
library(here)
library(kableExtra)
library(gt)
library(patchwork)
library(likert)
library(viridis)
# r_refs("references.bib")

@@

```{r include=FALSE}
# List of used programming languages and their counts text
language_table <-
  processed %>% 
  rename(lang = programming_language) %>% 
  separate_rows(lang, sep = ",") %>% 
  count(lang) %>% 
  filter(!is.na(lang)) %>% 
  arrange(desc(n)) %>% 
  mutate(lang_n = glue::glue("{lang} (n = {n})")) %>% 
  pull(lang_n) %>% 
  glue::glue_collapse(., sep = ", ", last = ", and ")

@@

We invited the ALSPAC mailing list to participate, which included 1148 email addresses. 54 emails bounced, leaving 1094 emails that went through. The survey was completed `r nrow(processed)` times and partially completed `r nrow(filter(processed, has_missing)) ` times, leading to a response rate of `r round(nrow(processed) / 1094 * 100)`% for completed surveys and `r round(nrow(filter(processed, has_missing)) / 1094 * 100)`% for incomplete surveys.[^1] The results presented in this manuscript only include completed surveys.[^2] The median time taken for complete survey responses was `r median(processed$duration_in_mins)` minutes (IQR: `r round(quantile(processed$duration_in_mins, .75), 1)` - `r round(quantile(processed$duration_in_mins, .25), 1)`).

Respondents published a median of `r median(processed$n_studies)` (IQR `r round(quantile(processed$n_studies, .75), 1)` - `r round(quantile(processed$n_studies, .25), 1)`) studies using preexisting observational data (Figure S1). They reported using the programming languages `r language_text` (Table S1). `r pull(filter(concerned, support == "positive"), percentage)`% of participants reported being more concerned, versus `r pull(filter(concerned, support == "negative"), percentage)`% who reported being less concerned, with research trustworthiness, bias, rigour, and reproducibility compared to what they think of as a typical research who uses preexisting observational data (Figure #).

```{r, include=FALSE}
# Concerned figure data preparation
concerned_plot_data <-
  processed %>% 
  select(concerned) %>% 
  mutate(
    concerned = factor(concerned, levels = c(
      "very much less concerned",
      "less concerned",
      "somewhat less concerned",
      "as concerned as a typical researcher in my field",
      "somewhat more concerned",
      "more concerned",
      "very much more concerned"
      )
    )
  )

@@

```{r include=FALSE}
willing <- support_percentage(
  processed,
  alspac_less_willing,
  c(
    "Strongly disagree",
    "Somewhat disagree",
    "Neither agree nor disagree",
    "Somewhat agree",
    "Strongly agree"),
  c(
    "I don't understand the question",
    "Unsure"
    )
  )

@@

```{r}
# Check if there is any missing and don't understand responses separately
alspac_missing_text <-
  processed %>% 
  select(contains("alspac_")) %>% 
  pivot_longer(
    cols = everything(),
    names_to = "item",
    values_to = "value"
    ) %>% 
  dplyr::filter(is.na(value) | value == "I don't understand the question" | value == "Unsure") %>% 
  mutate(item = str_to_title(str_remove(item , "^[^_]*_"))) %>% 
  replace_na(list(value = "Missing")) %>% 
  group_by(item , value) %>% 
  summarise(
    n = n()
  ) %>% 
  ungroup() %>% 
  mutate(text = paste(value, "=", n))

>>>>

```{r setup, include = FALSE, warning=FALSE, message=FALSE}
# Load pacakges
library("papaja")
library(tidyverse)
library(here)
library(kableExtra)
library(gt)
library(patchwork)
library(likert)
library(viridis)
# r_refs("references.bib")

@@

```{r include=FALSE}
# List of used programming languages and their counts text
language_text <-
  processed %>% 
  rename(lang = programming_language) %>% 
  separate_rows(lang, sep = ",") %>% 
  count(lang) %>% 
  filter(!is.na(lang)) %>% 
  arrange(desc(n)) %>% 
  mutate(lang_n = glue::glue("{lang} (n = {n})")) %>% 
  pull(lang_n) %>% 
  glue::glue_collapse(., sep = ", ", last = ", and ")

@@

We invited the ALSPAC mailing list to participate, which included 1148 email addresses. 54 emails bounced, leaving 1094 emails that went through. The survey was completed `r nrow(processed)` times and partially completed `r nrow(dplyr::filter(processed, has_missing)) ` times, leading to a response rate of `r round(nrow(processed) / 1094 * 100)`% for completed surveys and `r round(nrow(filter(processed, has_missing)) / 1094 * 100)`% for incomplete surveys.[^1] The results presented in this manuscript only include completed surveys.[^2] The median time taken for complete survey responses was `r median(processed$duration_in_mins)` minutes (IQR: `r round(quantile(processed$duration_in_mins, .75, na.rm = TRUE), 1)` - `r round(quantile(processed$duration_in_mins, .25, na.rm = T), 1)`).

Respondents published a median of `r median(processed$n_studies)` (IQR `r round(quantile(processed$n_studies, .75, na.rm = TRUE), 1)` - `r round(quantile(processed$n_studies, .25, na.rm = TRUE), 1)`) studies using preexisting observational data (Figure S1). They reported using the programming languages `r language_text` (Table S1). `r pull(filter(concerned, support == "positive"), percentage)`% of participants reported being more concerned, versus `r pull(filter(concerned, support == "negative"), percentage)`% who reported being less concerned, with research trustworthiness, bias, rigour, and reproducibility compared to what they think of as a typical research who uses preexisting observational data (Figure #).

```{r, include=FALSE}
# Concerned figure data preparation
concerned_plot_data <-
  processed %>% 
  select(concerned) %>% 
  mutate(
    concerned = tolower(concerned),
    concerned = factor(concerned, levels = c(
      "very much less concerned",
      "less concerned",
      "somewhat less concerned",
      "as concerned as a typical researcher in my field",
      "somewhat more concerned",
      "more concerned",
      "very much more concerned"
      )
    )
  )

@@

```{r include=FALSE, warning=FALSE, message=FALSE}
willing <- support_percentage(
  processed,
  alspac_less_willing,
  c(
    "Strongly disagree",
    "Somewhat disagree",
    "Neither agree nor disagree",
    "Somewhat agree",
    "Strongly agree"),
  c(
    "I don't understand the question",
    "Unsure"
    )
  )

@@

```{r warning=FALSE, message=FALSE}
# Check if there is any missing and don't understand responses separately
alspac_missing_text <-
  processed %>% 
  select(contains("alspac_")) %>% 
  pivot_longer(
    cols = everything(),
    names_to = "item",
    values_to = "value"
    ) %>% 
  dplyr::filter(is.na(value) | value == "I don't understand the question" | value == "Unsure") %>% 
  mutate(item = str_to_title(str_remove(item , "^[^_]*_"))) %>% 
  replace_na(list(value = "Missing")) %>% 
  group_by(item , value) %>% 
  summarise(
    n = n()
  ) %>% 
  ungroup() %>% 
  mutate(text = paste(value, "=", n))

### 2023-03-14 preprocessing/ecaw_raw_processed_preprocessing.Rmd
initial draft of the manuscript with the results

```{r}
raw <-
  raw %>% 
    # dropping those questions that were open ended or conditional on other responses or irrelevant
    # flag those responses that has any missing values
    mutate(
      has_missing = case_when(
        if_any(
          c(
            -start_date,
            -end_date,
            -status,
            -progress,
            -duration_in_seconds,
            -finished,
            -recorded_date,
            -distribution_channel,
            -user_language,
            -programming_language_other,
            -unsure_explain,
            -drawback_ecaw,
            -suggestions,
            -comments
            ),
          .fns = is.na) ~ 1L,
        TRUE ~ 0L
        )
      )
```

>>>>

```{r}
raw <-
  raw %>% 
    # dropping those questions that were open ended or conditional on other responses or irrelevant
    # flag those responses that has any missing values
    mutate(
      has_missing = case_when(
        if_any(
          c(
            -start_date,
            -end_date,
            -status,
            -progress,
            -duration_in_seconds,
            -finished,
            -recorded_date,
            -distribution_channel,
            -user_language,
            -programming_language_other,
            -unsure_explain,
            -drawback_ecaw,
            -suggestions,
            -comments
            ),
          .fns = is.na) ~ TRUE,
        TRUE ~ FALSE
        )
      )
```
